%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for jas Osborne
\documentclass[margin,line]{resume}
\usepackage{hyperref}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large James Ellis Osborne III}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    2183 Lansill Rd                         \hfill mobile: +1 859 HAX0RED\\
    Lexington, Ky 40504                     \hfill email: busytoby@gmail.com\vspace{-6mm}\\%

    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Kentucky}, Lexington, Kentucky, United States \\
    \textsl{Bachelor of Science, Computer Science/Linguistics} \hfill \textbf{ August 1999 - May 2004}\vspace{-4mm}\\%
    \begin{list2}
        \item GPA: 3.82
        \item Recipient of 2003 "Buzz" Award, NASA SAS (Software Assurance Symposium), for "Robust Requirements 
              Tracing via Information Retrieval" project, (with Jane Hayes and Alex Dekhtyar)
        \item Recipient of 2002 Alltel Networking Scholarship
    \end{list2}\vspace{-2.5mm}


    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{EAS Technologies}, Lexington, Ky \\
    \textsl{Senior Applications Architect} \hfill \textbf{April 2008 - Present}\vspace{2mm}\\%
    Developed web-based, source-independent Form Document processing system in PHP 
    using object recognition techniques to allow automated parsing and auto-filling 
    of arbitrary document types.  Application was used to replace a manual process 
    of phone interviews and manual data entry into PDF forms. Also responsible for 
    all maintenance and support of internal and public-facing servers. 

    \textbf{Hewlett-Packard (Formerly Exstream Software LLC)}, Lexington, Ky  \\
    \textsl{Software Build Engineer} \hfill \textbf{October 2006 - April 2008}\vspace{2mm}\\%
    Developed a cross-platform distributed build system in Java and Python to support 
    synchronously deployed builds across Solaris, HPUX, AIX, Linux, AS/400, OS/390, and 
    MVS/Unix systems reducing overall build time from days to hours. Assisted in implementation 
    of automated build configuration system. Developed Installshield installer projects and 
    Java-based dynamic code generation tools to support installer builds for 22 maintained 
    product configurations on a daily release cycle from a single installer code base. Reduced 
    time spent on installer maintenance/testing by a factor of 30. Responsible for oversight
    of Unix systems build tools and procedures.  

    \textbf{Amazon.com}, Lexington, Ky \\
    \textsl{Systems Engineer} \hfill \textbf{May 2006 - October 2006}\vspace{2mm}\\%
    Lead engineer and IT Coordinator for Lexington FC.  Team lead and primary technician for 
    Red Hat Enterprise Linux upgrades in Lexington, Hebron (Ky), and Inverclyde (Scotland) 
    Fulfillment centers.  Directly responsible for 24/7 support of over 2000 nodes in Amazon's 
    largest fulfillment center.  Responsible for training and skill development of five person 
    support team. Utilised extensive Cisco, server hardware, and Linux knowledge to determine 
    and coordinate fixes for critical issues. 

    \textbf{Center for Visualization and Virtual Environments}, Lexington, Ky  \\
    \textsl{Network/Systems Administrator} \hfill \textbf{June 2003 - May 2006}\vspace{2mm}\\%
    Lead administrator of a heterogeneous research environment.  Developed shell-based rapid 
    deployment tool to support low-bandwidth synchronous system imaging. Responsible for 
    supervision and task delegation to support team, inventory tracking, vendor/manufacturer
    communications, equipment specification and purchase, and physical security monitoring
    Responsible for creating and testing custom Debian-based Linux distribution packages and 
    clone/install-media for rapid deployment. 

    \textbf{University of Kentucky Department of Computer Science}, Lexington, Ky \\
    \textsl{Software Architect} \hfill \textbf{May 2002 - January 2003}\vspace{2mm}\\%
    Sole developer of an experimental NASA funded linguistic analysis tool for automated 
    software requirements tracing using GNU C++ in a Linux environment.
  
    \textbf{Lumenware LLC}, Lexington, Ky \\
    \textsl{Software Developer} \hfill \textbf{January 2002 - May 2002}\vspace{2mm}\\%
    Developed a cross-platform multi-cast network protocol for arbitrary XML-based communications 
    for service advertisement and discovery under Linux,  Solaris, and Windows. Gained experience 
    with Object Oriented Programming in C++, Java, thin-client architectures, XML, UPNP/SSDP, and 
    multi-cast network protocol design.\newpage

    \textbf{Proud Marys Booksellers}, Shelbyville, Ky \\
    \textsl{Technical Coordinator} \hfill \textbf{February 1996 - January 2001}\vspace{2mm}\\%
    Responsible for support, maintenance, and Internet presence of  bookseller. Designed and 
    maintained a database cataloguing over 500,000 rare and out-of-print books and textbooks for 
    sale.  Responsible for appraisal and sales strategy of all non-English material. Developed Java 
    and PHP based terminal software for inventory, sales, and search of multiple database sources 
    of rare and out-of-print books.

    %__________________________________________________________________________________________________________________
    % Skillz
    \section{\mysidestyle Interests\\and\\Projects} 
    \textsl{Ongoing Open Source Contributions}\vspace{-4mm}\\%
    \begin{list2}
        \item Gitrbug/DMP, a content-aware distributed filesharing application/protocol, PHP, pre-alpha
        \item Fableton, a topic-trending personality driven MegaHAL chatbot for Twitter, achieved 9000 followers 
              in 3 months before the project was halted, \href{http://lexvegas.org/fableton.tgz}{Python Source}
        \item Origami.BTree, a drop-in replacement for CakePHP's standard TreeBehaviour for exponential speed 
              improvement with large data sets, PHP, pending RFC at 
              \href{http://code.cakephp.org/tickets/view/78}{code.cakephp.org}
        \item Origami.DataStore, Data-aware Meta-Storage Engine for CakePHP, Presented at CakeFest \#2, 
              December 2008 Buenos Aires, Argentina, \href{http://thechaw.com/origami/source/trunk}{PHP Source}
        \item Indiepedia.org, Independent Music Symantic Wiki project for cataloguing relationships within musical 
              groups and artists for statistical representation, Perl, currently offline/stalled due to 
              disappearance of co-founder
        \item At least 1 line of code contributed to: Nicotine+, LiveJournal, Logjam, Openfire, Linux and FreeBSD 
              kernels, Amarok, CakePHP, B2, Wordpress, PtokaX, Verlihub, Postfix, and Exim
    \end{list2}

    \textsl{Areas and Paradigms}\vspace{-4mm}\\%
    \begin{list2}
        \item MVC, C/S, and Distributed Computing Application Models
        \item Dynamic and Genetic Code Generation
        \item Robotics and Machine Vision and Learning
        \item P2P, Social, and Music Oriented Software Development
    \end{list2}

    \textsl{Environments}\vspace{-4mm}\\%
    \begin{list2}
        \item Debian Linux, Enlightenment 17, Emacs, gdb, Opera/Dragonfly, Firefox/Firebug
        \item Python, PHP, C, Lua, C++, Java, Awk, Lisp, FORTRAN, Perl (in order of preference/comfort)
    \end{list2}

    \textsl{Administration Experience}\vspace{-4mm}\\%
    \begin{list2}
        \item Full-lifecycle administration of Linux, Solaris, AIX, HPUX, OS/390, and AS/400 MVS/Unix
        \item Familiar with administration as well as implementation and forensic details of most common protocols and daemons
    \end{list2}

    \textsl{Analogue Circuit Design and Atmel Microcontroller Programming}\vspace{-4mm}\\%
    \begin{list2}
        \item Analogue projects have included Distortion, Tremelo, and Boost guitar pedal construction from public-domain schematics
        \item Digital projects have included program design for camera-based object and facial recognition, motor-control
              systems for robotic mobility, and data-capture systems for physical modelling
    \end{list2}

    \textsl{Linguistics}\vspace{-4mm}\\%
    \begin{list2}
        \item Familiar with modern and historical West Germanic and Latinate language morphologies and syntax and most non-Asian phonologies
        \item Competent in Spoken English, French, and Spanish
        \item Comfortable translating modern and historical documents in Latinate and West Germanic languages
    \end{list2}

    \textsl{Music/Sound Engineering}\vspace{-4mm}\\%
    \begin{list2}
        \item Musical and/or Engineering credit on over 20 releases by The Melody Function, The Ideal Free Distribution, 
              Avril en Mai, The Fucking Jacobs, and The Apples in Stereo
        \item Over 15 years playing guitar and electric bass
        \item Competent with ProTools, Live, Goldwave, and Sony software products
        \item Familiar with studio and live hardware and software effects
    \end{list2}

    \section{\mysidestyle Publications}
    \textbf{Improving Requirements Tracing via Information Retrieval}, Jane Huffman Hayes, Alex Dekhtyar, and James Osborne,
    In Proceedings, 11th International Requirements Engineering Conference (RE 2003), pp. 151-161, 
    September 2003, Monterey Bay, CA.\vspace{-3mm}\\%

    \hfill \href{http://lexvegas.org/resume.tgz}{\LaTeX{} Source}
%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

